Predicting Remaining Useful Life of NASA Aircraft Engines

### 2025-02-17 index.qmd
2/17 updates

---
title: "Predicting Remaining Useful Life of NASA Aircraft Engines"
subtitle: "Using Cox Proportional Hazards Model"
author: "Jayme Reed & Brad Paton (Advisor: Dr. Cohen)"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: Capstone Projects in Data Science
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

@@

Cox proportional hazards (CPH) models are statistical regression models specializing in
modeling time-to-event predictions with survival data. Survival data is data with a value
for time and an event. For example, in a study investigating the survival likelihood of
mechanical equipment time would begin when the equipment begins functioning and would
conclude in the event the equipment stops functioning. [@Smith2003] CPH models can use
single or multiple covariates as a means of creating predictions until failure and are
capable of dealing with survival data that contains censored data as well.[@Seung2023]
Censored data is when the information about an individual in a study is only known for a
certain period of time, such as the length of the study [@klein2005, 1]. The models also
have the advantage of being semi-parametric which allows more flexibility as compared to
other models. [@Ming-Chiang2014]

>>>>

---
title: "Predicting Remaining Useful Life of NASA Aircraft Engines"
subtitle: "Using Cox Proportional Hazards Model"
author: "Jayme Reed & Brad Paton (Advisor: Dr. Cohen)"
date: '`r Sys.Date()`'
format:
  html:
    theme: spacelab
    toc: true
    toc-depth: 3
    code-fold: true
course: Capstone Projects in Data Science
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

@@

Cox proportional hazards (CPH) models are statistical regression models specializing in
modeling time-to-event predictions with survival data. Survival data is data with a value
for time and an event.[@Abeysekera2009] For example, in a study investigating the survival likelihood of
mechanical equipment time would begin when the equipment begins functioning and would
conclude in the event the equipment stops functioning. [@Smith2003] CPH models can use
single or multiple covariates as a means of creating predictions until failure and are
capable of dealing with survival data that contains censored data as well.[@Seung2023]
Censored data is when the information about an individual in a study is only known for a
certain period of time, such as the length of the study [@klein2005, 1]. The models also
have the advantage of being semi-parametric which allows more flexibility as compared to
other models. [@Ming-Chiang2014]
